---
title             : "APA Midterm"
shorttitle        : "Music Memory"

author: 
  - name          : "Angelina Vasquez"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : ""
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Brooklyn College"
  - id            : "2"
    institution   : ""




authornote: |
  A Brooklyn College Graduate student. Also, a John Jay College research assistant.

  Enter author note here.

abstract: |
  Five-month old infants listened to songs sung by their parent, a toy,or someone unfamiliar for one to two week period. These songs had the same lyrics and rhythms. However, the melodies were different. The researchers tested the infants selected attention when a random person sang the song they were familiar with and the song they were not. The results indicated that infants paid more attention to the song they were familiar with, and that exposure time predicted preference time. This suggests that melodies may carry social meanings for infants.    
  

  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "music,social cognition,memory,infant development,open data"
wordcount         : "X"

bibliography      : ["r-references.bib","CopyOfRef.bib"] #make new r script with my ref.bib in bracket,add""ref.bib" click bibtex version to add to script in code

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(data.table)

all_data <- fread("https://raw.githubusercontent.com/CrumpLab/statisticsLab/master/data/MehrSongSpelke2016.csv")
library(summarytools)
view(dfSummary(all_data))
library(dplyr)
experiment_one <- all_data %>% filter(exp1==1)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants
The participants were 32 infants and both their parents. However, only one of the paretns was active in their participation.

## Material
The materials for this study consisted of two adpated versions of lullabies from folk collections.These were also provided through a website with the recordings of the songs and printed versions of the lyrics. The advanced measures of music audiation assesment was also used.

## Procedure
This study was compromised of 4 overall experiments. During the first lab visit for experiment 1, parents were randomly assigned to either music condition. Once they got their condition with the song they would have to sing, they were given a music lesson. Parents were also instructed to visit a website that had the recording of the song so they could practice. Lastly, parents completed an standard assesment for music perception skill.

Everyday, participants were emailed a survey to assess the number of times the infant heard the song. The researchers took the average of those surveys and mulitpled it by the days of the study to determine how much exposure they had to that song.

On the last day of the study, the infants were given an attention test. They sat on their parent's lap while they watched a projection screen with another two people  on it singing the familar song and unfamilar song.The first were presented with vidoe recordings of the individuals smiling. Then they viewed the recordings with the individuals singing. Lastly, the viewed the the first recording again of the smiling individuals.

In experiment two, the overal procedure was replicated fro, experiment 1. However, instead of having the parent sing the song to them duriing the study, they had a toy with a reocding of the song sing it during the study.

In experiment three, the overall procedure was replicated fro, experiment 1. However, instead of having the parent sing the song to them duriing the study, they had a friendly adult.


## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.
```{r}
baseline <- experiment_one$Baseline_Proportion_Gaze_to_Singer
mean(baseline)
sd(baseline)
hist(baseline)
```
T-test analysis
```{r}
t.test(baseline, mu=.5)
```
So, there we have it. We did a one-sample t-test. Here’s how you would report it, t(31) = .67, p = .505. Or, we might say something like:

During the baseline condition, the mean proportion looking time toward the singer was .52, and was not significantly different from .5, according to a one-sample test, t(31) = .67, p = .505.

###power anaylisis probablity finding something given it is there how big is it how many subjects there is the pwr package to do analysis go to github simulation presentations for power analysis


# Results
###apa print function will make a table of the data you ran(anova table) if you write something and then put`r write something other tick-that treats as r code some this test significant tick r F value p value tick-----a=1,2,3,sapply(a,fun=function(x)return (x+1))

```{r myfig, fig.cap="This is histo"}
a<- rnorm(100,0,1)
hist(a)
```


# Discussion


\newpage

# References
Mehr, S. A., Song, L. A., & Spelke, E. S. (2016). For 5-month-old infants, melodies are social. Psychological Science, 27(4), 486-501.
```{r create_r-references}
r_refs(file = "r-references.bib")

```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
