---
title             : "APA Midterm"
shorttitle        : "Music Memory"

author: 
  - name          : "Angelina Vasquez"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : ""
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Brooklyn College"
  - id            : "2"
    institution   : ""




authornote: |
  A Brooklyn College Graduate student. Also, a John Jay College research assistant.

  Enter author note here.

abstract: |
  Five-month old infants listened to songs sung by their parent, a toy,or someone unfamiliar for one to two week period. These songs had the same lyrics and rhythms. However, the melodies were different. The researchers tested the infants selected attention when a random person sang the song they were familiar with and the song they were not. The results indicated that infants paid more attention to the song they were familiar with, and that exposure time predicted preference time. This suggests that melodies may carry social meanings for infants.    
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "music,social cognition,memory,infant development,open data"
wordcount         : "X"

bibliography      : ["r-references.bib","CopyOfRef.bib"] #make new r script with my ref.bib in bracket,add""ref.bib" click bibtex version to add to script in code

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(data.table)

all_data <- fread("https://raw.githubusercontent.com/CrumpLab/statisticsLab/master/data/MehrSongSpelke2016.csv")
library(summarytools)
view(dfSummary(all_data))
library(dplyr)
experiment_one <- all_data %>% filter(exp1==1)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.
```{r}
baseline <- experiment_one$Baseline_Proportion_Gaze_to_Singer
mean(baseline)
sd(baseline)
hist(baseline)
```
T-test analysis
```{r}
t.test(baseline, mu=.5)
```
So, there we have it. We did a one-sample t-test. Here’s how you would report it, t(31) = .67, p = .505. Or, we might say something like:

During the baseline condition, the mean proportion looking time toward the singer was .52, and was not significantly different from .5, according to a one-sample test, t(31) = .67, p = .505.

###power anaylisis probablity finding something given it is there how big is it how many subjects there is the pwr package to do analysis go to github simulation presentations for power analysis


# Results
###apa print function will make a table of the data you ran(anova table) if you write something and then put`r write something other tick-that treats as r code some this test significant tick r F value p value tick-----a=1,2,3,sapply(a,fun=function(x)return (x+1))

```{r myfig, fig.cap="This is histo"}
a<- rnorm(100,0,1)
hist(a)
```


# Discussion


\newpage

# References
Mehr, S. A., Song, L. A., & Spelke, E. S. (2016). For 5-month-old infants, melodies are social. Psychological Science, 27(4), 486-501.
```{r create_r-references}
r_refs(file = "r-references.bib")

```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
